``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics

### 2015-04-10 manuscript.tex
Updates from ShareLaTeX

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.9}
\usepackage{picture}
\newcommand{\kw}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(50,3)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

@@

\begin{document}
  \title{An Instance Based Reasoning for Empirical Transfer Learning}

  \author{\IEEEauthorblockN{Rahul Krishna}
    \IEEEauthorblockA{
      North Carolina State University, USA\\
      rkrish11@ncsu.edu}
    \and
    \IEEEauthorblockN{Tim Menzies}
    \IEEEauthorblockA{North Carolina State University, USA\\
      tim.menzies@gmail.com}}

@@

\begin{figure}[htbp!]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
\begin{enumerate}
\item Find two distant points in that population; call them the {\em east} and {\em west} poles. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the median $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}

>>>>

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.9}
\usepackage{picture}
\newcommand{\kw}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(50,3)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

@@

\begin{document}
  \title{``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}

  \author{\IEEEauthorblockN{Rahul Krishna, Tim Menzies, Xipeng Sheng}
    \IEEEauthorblockA{
      Computer Science, North Carolina State University, USA\\
  i.m.ralk, tim.menzies, xipengshen@gmail.com}\and
  \IEEEauthorblockN{Andrian Marcus}
   \IEEEauthorblockA{
      Computer Science, University of Texas, Dallas,  USA\\
  amarcus@utdallas.edu}}

@@

\begin{figure}[htbp!]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
\begin{enumerate}
\item Find the two most distant points in a given population; say {\em east} and {\em west}. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the median $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}
